Modelling the emergence of whisker barrels

### 2020-07-10 paper/briefpaper/brief.tex
Modifies paper with row trimming result

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png} \captionof{figure}{
    \MPthreePred{Simulating altered barrel development.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by
      reducing the competitiveness, $\epsilon$, of the one projection. For C3
      only, $\epsilon$ was mutiplied by $m\in(0,1)$. The pattern shown is that
      formed after 30000 steps with $m=0.86$, which reduces the size of the C3
      field to 65\% of its original size, matching the average barrel area
      reduction observed by }
    \citealp{kossut_effects_1992}. \MPthreePred{\textbf{D} The area of the C3
      barrel reduces as $m$ is reduced, whereas the mean area of neighbouring
      barrels (B3, C2, C4, D2 \& D3, grey circles) increases. The dotted grey
      line indicates $m=0.86$ for comparison with panel C.}}
  \label{fig:fgf8}
\end{center}

\MPthreePred{Finally, to investigate the response of the model to
  environmental manipulation, we simulated a whisker deprivation
  experiment. In a critical period comprising the first postnatal days,
  removal of the whiskers by electrocauterization, plucking, or trimming leads
  to observable changes in brain structures, including the barrel
  field~\citep{jeanmonod_mouse_1981}. Amongst other changes, deprivation of
  individual whiskers, or an entire row of whiskers leads to smaller
  barrels~\citep{kossut_effects_1992,loos_somatosensory_1973}. We simulated
  trimming of the individual whisker C3 during the critical period by reducing
  the competitiveness of the C3 thalamocortical projection, $\epsilon$. As a
  result, the corresponding field size was smaller (Fig.\,\ref{fig:fgf8}C),
  and the size of the fields representing the neighbours of C3 increased in
  size. A reduction in area to 65\%, comparable to that induced by
  \citealp{kossut_effects_1992}, was obtained in simulation when $\epsilon$
  was reduced to 86\% (Fig.\,\ref{fig:fgf8}D.), and the C3 barrel disappeared
  altogether when $\epsilon$ was less than half of its original value.}

>>>>

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png} \captionof{figure}{
    \MPthreePred{Simulating altered barrel development.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by
      reducing the competitiveness, $\epsilon$, of the one projection. For C3
      only, $\epsilon$ was mutiplied by $m\in(0,1)$. The pattern shown is that
      formed after 30000 steps with $m=0.86$, which reduces the size of the C3
      field to 65\% of its original size, matching the average barrel area
      reduction observed by }
    \citealp{kossut_effects_1992}. \MPthreePred{\textbf{D} The area of the C3
      barrel (black squares) reduces as $m$ is reduced, whereas the mean area of neighbouring
      barrels (B3, C2, C4, D2 \& D3, grey circles) increases. The dotted grey
      line indicates $m=0.86$ for comparison with panel C. If the $\epsilon$
      value is instead reduced for \emph{all} row C projections (including the interstitial
      $\gamma$ projection), the mean row C barrel area is only slightly
      reduced (light grey triangles). In this case, the mean row C area at
      $m=0.86$ is 91\% of that for $m=1$.}}
  \label{fig:fgf8}
\end{center}

\MPthreePred{Finally, to investigate the response of the model to
  environmental manipulation, we simulated a whisker deprivation
  experiment. In a critical period comprising the first postnatal days,
  removal of the whiskers by electrocauterization, plucking, or trimming leads
  to observable changes in brain structures, including the barrel
  field~\citep{jeanmonod_mouse_1981}. Amongst other changes, deprivation of
  individual whiskers leads to smaller
  % loos_somatosensory_1973 for row cauterization
  barrels~\citep{kossut_effects_1992}. We simulated
  trimming of the individual whisker C3 during the critical period by reducing
  the competitiveness of the C3 thalamocortical projection, $\epsilon$. As a
  result, the corresponding field size was smaller (Fig.\,\ref{fig:fgf8}C),
  and the size of the fields representing the neighbours of C3 increased in
  size. A reduction in area to 65\%, comparable to that induced by
  \cite{kossut_effects_1992}, was obtained in simulation when $\epsilon$
  was reduced to 86\% (Fig.\,\ref{fig:fgf8}D), and the C3 barrel disappeared
  altogether when $\epsilon$ was less than half of its original value.}

\MPthreePred{Although individual whisker trimming reduces barrel size, if an
  entire row is trimmed, barrel sizes for the trimmed row are not obviously
  changed \citep{land_metabolic_1985}. We investigated with a simulation in
  which we varied $\epsilon$ for all of the row C projections.  Although the
  barrels which formed for row C did show some reduction in area
  (Fig.\,\ref{fig:fgf8}D), this reduction was small when compared with the
  individually trimmed C3 simulation. If the effect of trimming any whisker is
  to reduce its $\epsilon$ (the competitiveness of its projection) to 86\% of
  its original value, then the model predicts that the cortical barrels for
  the trimmed C row will retain 91\% of their area.}
